---
poster_height: "841mm"
poster_width: "1189mm"
title_textsize: "90pt"
title: <tt>nash:</tt> using Game Theory towards sustainable resource exploitation.
author:
  - name: T.J. Del Santo O'Neill
    affil: 1</br>
    email: t.j.delsantooneill@qmul.ac.uk
    twitter: TJO_Neill
    github: ThomasDelSantoONeill
    main: true
  - name: '</br><font size="+4">Supervisors:</font>'
    main: false
  - name: '</br></br><font size="+4">A.G. Rossberg</font>'
    main: false
    affil: 1
  - name: '<font size="+4">,&nbsp;L. Chittka</font>'
    main: false
    affil: 1
  - name: '<font size="+4">&nbsp;and R.P. Thorpe.</font>'
    main: false
    affil: 2
affiliation:
  - num: 1
    address: <i class="fa fa-university"></i> School of Biological and Chemical Sciences, Queen Mary University of London (UK).
  - num: 2
    address: <i class="fa fa-university"></i> Centre for Environment, Fisheries and Aquaculture Science, Lowestoft (UK).
main_findings:
  - '<p style="text-align:center">The natural **solution** for optimal **harvesting** of **interacting** fish stocks is the **Nash equilibrium**. Our R package **nash** facilitates its computation for any arbitrary **user**-defined **ecosystem model**.</p>'
logoleft_name: |
  <img src="C:/Users/delsa/Documents/SBCSposter/Poster_files/QMlogo.svg" id="Logos">
main_fontfamily: "Inconsolata"
main_width: 0.4
main_textsize: "105pt"
reference_textsize: "16pt"
output: 
  posterdown::posterdown_betterland:
    self_contained: false
    pandoc_args: --mathjax
    highlight: haddock
    number_sections: false
link-citations: yes
primary_colour: "#009999"
secondary_colour: "#000999"
bibliography: ppt.bib
csl: bib.sty
---
<style>
#Logos {
  top: 2850px;
  left: 1367.5px;
  position: fixed;
}
#nashlogo {
  top: 5px;
  left: 1500px;
  position: fixed;
}
#Methods {
  width: 900px;
  height: 400px;
}
p.caption {
  margin-top: -20pt;
  margin-bottom: 0;
}
p {
    margin-top:-20px;
}
</style>

```{r, include=FALSE}
knitr::opts_chunk$set(results = 'asis',
                      echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html") 
```

# Motivation

Our research aims to contribute towards the realisation of the 14th Sustainable Development Goal subscribed by the United Nations in the [2030 Agenda for Sustainable Development](https://sdgs.un.org/2030agenda); particularly, on how to sustainably extract marine living resources through fishing [@Duarte2020].

Current management advice is provided on a *species-by-species* (SS) basis relative to the "Maximum Sustainable Yield" (MSY) target [@CFP2013;@Act2020]. Nonetheless, in marine systems species rarely (if at all) occur in isolation [@Menegotto2018], sharing the factors that regulate their growth and (more often than not) feeding upon one another. Within this more realistic *multispecies* (MS) setting, applying SS-MSY based policies carries great risk of stock collapse [@May1979]. 

In our research, we use abstract ecosystem models where trophic interactions are accounted for to obtain optimal harvesting rates for all exploited stocks in such a way that changes in any single rate cannot increase the long-term yield for that stock [@Farcas2016]. This solution is by definition a *Nash Equilibrium* (NE) [@Nash1951] in non-cooperative game theory where rational players maximise their benefits. 

# Under the hood

Here we present `nash`, an `R` package [@R2020] that computes NE harvesting rates ($\mathbf{F}$) for ecological models of the form:
\begin{equation}
  \frac{d\mathbf{B}}{dt}=\mathbf{f}(\mathbf{B})\circ \mathbf{B}-\mathbf{F}\circ\mathbf{B}.
  (\#eq:1)
\end{equation}
The user defines an `R` function that contains equation \@ref(eq:1) alongside an integration routine to solve it, taking $\mathbf{F}$ as input and returning long-term yields as output. 

The `nash` function will then approximate equation \@ref(eq:1) near equilibrium dynamics by a multispecies Lotka-Volterra (LV) model, for which the NE can be computed analytically and so a first estimation of optimal $\mathbf{F}$ obtained. Subsequently, an updated LV approximation is calculated near the equilibrium given by this new $\mathbf{F}$. `nash` will then re-compute the NE starting a new iteration until a (user-adjustable) convergence threshold for $\mathbf{F}$ is reached.

# Usage Sample

`nash` implementation was successfully tested for several complex ecosystem models. Here we showcase its application to the North Sea food web where optimal Nash Equilibrium harvesting rates are found:

```{r , out.width='80%'}
knitr::include_graphics("C:/Users/delsa/Documents/SBCSposter/Results.svg")
```

# Conclusion

Single species modelling was the most parsimonious approach to theoretically guide management in the 20th century. Nonetheless, the amount of anthropogenic stressors natural resources are subjected too at present requires more accurate model formulations. `nash` streamlines the computation of a promising multispecies Maximum Sustainable Yield objective for holistic ecosystem models.


# References
